---
title: "R Notebook:Workflow (Ch. 4, 6, 8)"
output: html_notebook
---

##Chapter 4: Workflow Basic
We can use R as a calcuator:
```{r}
(1/200*30)
```

We can create objects and assignments with <-
```{r}
(x<-3*4)
```

```{r}
this_is_a_really_long_name <- 2.5
this_is_a_really_long_name
```

```{r}
r_rocks <- 2^3
```

R is case sensitive and typos matter

Looking at functions  
>You can start typing a funtion then press tab to show possible completions as well as listing the function's arguments and purpose.

```{r}
seq(1, 10)
```

```{r}
x <- "hello world"
```

Add () around a funcion to "print to screen" the answer
```{r}
(y <- seq(1, 10, length.out = 5))
```

Look at all your objects in the environment tab

###Practice

1. This code does not work because the i in the second line of code does not match the line above.
2. Fix the code
```{r}
library(tidyverse)

ggplot(data = mpg)  
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
```

3. Alt + Shift + K opens up a shortcuts menu.

---

##Chapter 6: Workflow Scripts

Open an R script file to give yourself more room when working with more complex graphics  
> Use Cmd/Ctl + Enter to execute the current R expression in the console  
> Use Cmd/Ctl + Shift + S to execute the complete script in one step

###Practice
1. In the upper right hand corner of the rmd file you can click on "Show document outline" and see all the headings and outline of your document
2. The RStudio diagnostics will report missing arguments, warn if variable has no definition in scope, warn is variable is defined but not used, provide R style diagnostics, and many other errors.

---

##Chapter 8: Workflow Projects

You should instruct RStudio not to preserve your workspace between sessions, and use these shortcuts instead
1. Press Cmd/Ctrl + Shift + F10 to restart RStudio.
2. Press Cmd/Ctrl + Shift + S to rerun the current script.

RStudio shows your current working directory at the top of the console and you can print it out by running getwd()
```{r}
getwd()
```

###Summary  
>Create an RStudio project for each data analysis project  
>Keep data files there  
>Keep scripts there; edit them, run them in bits or as a whole  
>Save your outputs (plots and cleaned data) there  
>Only ever use relative paths, not absolute paths